Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-28 main-disk-model.tex
minor- changed typo
minor

@@

Furthermore, we place ourselves in a context where we do not have perfect knowledge
of the task parameters ($w_u$ and $m_u$) before the tasks start their execution,
but only estimates~\cite{rahman2013,GARG2015256}.  
%. \AB{Add motivation: related work with variable task durations for instance...}
Hence, scheduling decisions are made on these estimated parameters, and
may be reconsidered at runtime when a task starts its execution and we know its exact parameters.

@@

The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_j$ ($1 \leq j \leq k$) has an individual memory of size $M_j$ and a speed~$s_j$.
All processors have access to a common disk space of unlimited size, but of much slower speed.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individual memory.
This data can later be read back into memory at any time, or transferred to another processor.

@@

    \[
        w_{real} = \frac{w_u}{s_j} * (1 + (m_i - M_j)/m_i ) * q_s.

    \]
where $q_s$ sit he slowdown coefficient.
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

The goal is to find a schedule of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized while
respecting memory constraints. \skug{do we still formulate it like that?}
    %If a processor runs out of memory to execute
%a task mapped on it, the schedule is said to be {\em invalid}.

Since tasks are subject to variability, we aim at minimizing the actual makespan
achieved at the end of the execution, while decisions may be taken building
on the estimated task parameters.

>>>>

\newcommand{\bw}{bw}
\newcommand{\br}{br}

@@

Furthermore, we place ourselves in a context where we do not have perfect knowledge
of the task parameters ($w_u$ and $m_u$) before the tasks start their execution,
but only estimates~\cite{rahman2013,GARG2015256}.  
%. \AB{Add motivation: related work with variable task durations for instance...}
Hence, scheduling decisions are made on these estimated parameters, and
may be reconsidered at runtime when a task starts its execution and we know its exact parameters.
\AB{Variability only on $w_u$ for now}

@@

The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_u$ ($1 \leq u \leq k$) has an individual memory of size $M_u$ and a speed~$s_u$.
All processors have access to a shared disk of unlimited size, where they can write
and read data: Processor~$p_u$ has a bandwidth $\bw_u$ (resp. $\br_u$) to write  (resp. read),
and hence it takes a time $\frac{c_{u,v}}{bw_u}$ to write the data produced for~$p_v$, 
if this data is evicted from memory.

%, but of much slower speed.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individual memory.
This data can later be read back into memory at any time, or transferred to another processor.

@@

    \[
        w_{real} = \frac{w_u}{s_j} \* (1 + (m_i - M_j)/m_i ) \* q_s.
    \]
where $q_s$ sit he slowdown coefficient.
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

The goal is to find a schedule of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized. 
\AB{no more memory constraint, now the lack of memory just slows down the execution, correct?
I'll probably add a few sentences here...}
% while respecting memory constraints. \skug{do we still formulate it like that?}
    %If a processor runs out of memory to execute
%a task mapped on it, the schedule is said to be {\em invalid}.

Since tasks are subject to variability, we aim at minimizing the actual makespan
achieved at the end of the execution, while decisions may be taken building
on the estimated task parameters.
\AB{Probably need to clarify offline vs online problem at some point...}
